
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 9: Visualization - Revealing a graph"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2021_assignment9.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


-------

1. Use the dataset by of covid 19 by WHO at https://covid19.who.int/WHO-COVID-19-global-data.csv. Find the three countries with the most numbers of deaths by Covid-19. 

Hint: 
```{r}
library(gganimate)
library(ggplot2)
library(tidyverse)
library(lubridate)

df <- read_csv('https://covid19.who.int/WHO-COVID-19-global-data.csv')

```


-  Use `filter` to select the most current date 
```{r}
df %>% group_by(Country) %>% filter(Date_reported == max(Date_reported))


```


-  Pipe with `arrange(-Cumulative_deaths)` to rank the data by the number of cumulative deaths
```{r}
df %>% arrange(-Cumulative_deaths)
```


2. Make a plot revealing the number of deaths in the three countries with the most numbers of deaths
```{r}
df1 <- df %>% filter(Date_reported >= "2021-10-20") %>% arrange(-Cumulative_deaths)
view(df1)
```
```{r}
df %>% filter(Country %in% c('United States of America', 'Brazil', 'India')) %>% ggplot(aes(y=Cumulative_deaths, x=Date_reported, color=Country)) + geom_line() + geom_point(size=3) + geom_text(aes(label = Cumulative_deaths), hjust = -.1, size=5)+ transition_reveal(Date_reported)
```

3. Create the new variable (column) `death_per_cases` recording the number of deaths per cases (Hint: divide cumulative deaths by cumulative cases).  What are the three countries with the highest deaths per cases? 
```{r}
df$death_per_cases <- df$Cumulative_deaths / df$Cumulative_cases

df2 <- df %>% filter(Date_reported >= "2021-10-20") %>% arrange(-death_per_cases)
```
The three countries with the highest deaths per cases are Yemen, Peru, and Mexico.

4. Make a plot revealing the number of deaths per cases of the US, Italy and Mexico. 
```{r}
df %>% filter(Country %in% c('United States of America', 'Italy', 'Mexico')) %>% ggplot(aes(y=death_per_cases, x=Date_reported, color=Country)) + geom_line() + geom_point(size=3) + geom_text(aes(label = death_per_cases), hjust = -.1, size=5) + transition_reveal(Date_reported)
```

5. Use `transition_reveal` to create three animated graph with the vaccination data at 

https://raw.githubusercontent.com/govex/COVID-19/master/data_tables/vaccine_data/us_data/time_series/vaccine_data_us_timeline.csv
```{r}
df_vac <- read_csv('https://raw.githubusercontent.com/govex/COVID-19/master/data_tables/vaccine_data/us_data/time_series/vaccine_data_us_timeline.csv')

#1st graph
df_vac %>% filter(Province_State %in% c('Massachusetts', 'California')) %>% filter(Vaccine_Type == 'All') %>% group_by(Date) %>% ggplot(aes(y=Doses_admin, x=Date, color=Province_State))+ geom_line()+ geom_point(size=3)+ geom_text(aes(label = Doses_admin), hjust = -.1, size=5) + transition_reveal(Date)

#2nd graph
df_vac %>% filter(Province_State %in% c('Massachusetts', 'California', 'New York')) %>% filter(Vaccine_Type == 'All') %>% group_by(Date) %>% ggplot(aes(y=Doses_admin, x=Date, color=Province_State))+ geom_line()+ geom_point(size=3)+ geom_text(aes(label = Doses_admin), hjust = -.1, size=5) + transition_reveal(Date)

#3rd graph
df_vac %>% filter(Province_State %in% c('Massachusetts', 'California', 'New York')) %>% filter(Vaccine_Type == 'All') %>% group_by(Date) %>% ggplot(aes(y=Stage_Two_Doses, x=Date, color=Province_State))+ geom_line()+ geom_point(size=3)+ geom_text(aes(label = Stage_Two_Doses), hjust = -.1, size=5) + transition_reveal(Date)
```


